Multi-target detection with application to cryo-electron microscopy

### 2019-03-01 inverse_problems/inverse_problems.tex
edits section 1

%The models we described so far assume a well-separated support. The separation condition can be alleviated by assuming a Poisson process. 
%We consider the following observation model. Let $X \in\RL$ be a random vector drawn from some fixed distribution.

\TODO{Careful that $\gamma$ changed by a factor of $L$: need to modify here too.} Specifically, for some parameter $\gamma > 0$, the total number of signal occurrences is drawn from a Poisson distribution with expectation $(N-L+1)\gamma$. For each occurrence, a starting location $i$ is drawn uniformly and independently at random from $\{0, \ldots, N-L\}$. Then, one of the signals $x_1, \ldots, x_K$ is selected independently at random from a fixed distribution and added to the observation $y$ with first entry positioned at $i$. 
By definition of the Poisson process, the entries of $s$ are independent and follow a Poisson distribution with expectation $\gamma$. In particular, this model allows for (additive) signal overlap. %In Section~\TODO{ref?}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.

>>>>

Specifically, 
 letting $s[i]$ be the number of signals starting at location $i$, ${s[i] \overset{i.i.d.}{\sim} \Poisson(\gamma / L)}$  for some parameter $\gamma > 0$. 
 Then, each of those $s[i]$ is chosen independently at random from a fixed distribution over $\{1,\ldots,K,\}$ and the corresponding
signal $x_1, \ldots, x_K$ is added to the observation $y$ with first entry positioned at $i$. 
As in the well-separated model, the autocorrelations under this model depend only on the signals and the parameter $\gamma$.

 %Note that the expected total number of signals occurring in $y$ is equal to $(N - L + 1)\gamma / L$, and consequently the total lengths of all signals (including overlaps) divided by $N$ is equal to
%
%\begin{align}
%\frac{N - L + 1}{N} \cdot L \cdot \frac{\gamma  }{L} 
%\quad \overset{N\to\infty}{\longrightarrow} \quad \gamma.
%\end{align}
%
%In particular, this model allows for (additive) signal overlap

%Specifically, for some parameter $\gamma > 0$, the total number of signal occurrences is drawn from a Poisson distribution with expectation $(N-L+1)\gamma$. For each occurrence, a starting location $i$ is drawn uniformly and independently at random from $\{0, \ldots, N-L\}$. 
%Then, one of the signals $x_1, \ldots, x_K$ is selected independently at random from a fixed distribution and added to the observation $y$ with first entry positioned at $i$. 
%By definition of the Poisson process, the entries of $s$ are independent and follow a Poisson distribution with expectation $\gamma$. In particular, this model allows for (additive) signal overlap. %In Section~\TODO{ref?}, we show that the autocorrelations of $y$ are nonetheless equivalent to those arising under our well-separated model above.

 %More precisely,
 %Therefore, in the large $N$ limit $\gamma$ may be interpreted as the signal density, as in the well-separated model.
